APPROPRIATE TITLE
========================================================

# Synopsis
Immediately after the title, there should be a synopsis which describes and summarizes your analysis in at most 10 complete sentences.

# Data Processing
describes (in words and code) how the data were loaded into R and processed for analysis. In particular, your analysis must start from the raw CSV file containing the data. You cannot do any preprocessing outside the document. If preprocessing is time-consuming you may consider using the cache = TRUE option for certain code chunks.
## raw csv file
Load the data and cache it.
```{r cache=TRUE}
data <- read.csv(bzfile("repdata-data-StormData.csv.bz2"))
```

## preprocessing
```{r}
str(data)
```

#Injuries per event
Let's calculate the numeber of injuries and death per event in the last years.
```{r cache=TRUE}
inj_event <- aggregate(INJURIES ~ EVTYPE, data=data, FUN=sum)
death_event <- aggregate(FATALITIES ~ EVTYPE, data=data, FUN=sum)
```
Let's visualize the results
```{r cache=TRUE}
head(inj_event)
head(death_event)
max(inj_event$INJURIES)
max(death_event$FATALITIES)
```

# Results
